\documentclass[twoside, leqno, twocolumn]{article}
\usepackage{ltexpprt}


\usepackage{fullpage} %[cm]
\usepackage{lmodern} % enhanced version of computer modern
\usepackage[T1]{fontenc} % for hyphenated characters
 \usepackage{amsmath}
 \usepackage{amssymb}
\usepackage{microtype}
\usepackage{enumerate}
\usepackage{ctable} % provides toprule, bottomrule, midrule
%\usepackage[ruled,linesnumbered]{algorithm2e}
% \usepackage{amsthm}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{breqn}
\DeclareCaptionType{copyrightbox}
\usepackage{color}
\newcommand{\expect}{\mathrm{Exp}}
\newcommand{\hide}[1]{}
%\newtheorem{theorem}{Theorem} % {\bfseries}{\itshape}
%\newtheorem{lemma}{Lemma}[section]{\bfseries}{\itshape}
% \theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
%\newdef{claim}{Claim}
%
%\theoremstyle{definition}
%\newtheorem{definition}[lemma]{Definition} % {\bfseries}{\itshape}
%
%\theoremstyle{remark}
\newtheorem{claim}[lemma]{Claim} % {\bfseries}{\itshape}
\newtheorem{observation}[lemma]{Observation} % {\bfseries}{\itshape}
%
\DeclareMathOperator*{\argmin}{arg\,min}
\newcommand{\opt}{\mathrm{OPT}}
\newcommand{\eopt}{E_{\mathrm{OPT}}}
\newcommand{\edeg}{e_{\mathrm{deg}}}
\newcommand{\prob}{\textsc{Spectral Radius Minimization}}
\newcommand{\degr}{\mathrm{d}}
\newcommand{\Vol}{\mathrm{Vol}}
\newcommand{\wmax}{w_{\max}}
\newcommand{\eps}{\epsilon}
\newcommand{\diff}{\textsc{diff}}
\newcommand{\intS}{\textsc{Int}}
\newcommand{\cost}{\textsc{cost}}
\newcommand{\elt}{\text{elt}}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\DeclareMathOperator*{\nodes}{nodes}
\DeclareMathOperator*{\walks}{walks}
\DeclareMathOperator*{\ct}{count}

\title{Set Summarization Problem}
%\author{}
%\date{}
%
\begin{document}
%\maketitle
%

%\section{Introduction}

\input{abstract.tex}
\input{introduction.tex}
\input{relatedwork.tex}
\input{preliminaries.tex}
\input{methods.tex}
\input{results.tex}
\input{conclusions.tex}

\section{Using a submodular maximization approach for SSP}
We consider $k=1$.
Let $\mathcal{S} = \{S_1,\ldots,S_m\}$ denote the $m$ sets, which are subsets of
a ground set $U$. $T\subseteq U$ is a given target set.  For a subset
$X\subseteq \mathcal{S}$, let $u(X)=\bigcup_{S\in X} S$ denote the union of all the
sets in $X$.  The SSP problem is to
find sets $X=\{S_{i_1},\ldots,S_{i_r}\}$ and $Y=\{S_{j_1},\ldots,S_{j_s}\}$ such that
\[
T= u(X) - u(Y)
\]
The cost of such a representation is $|X|+|Y|$.

Let $\mathcal{S}_T=\{S\in\mathcal{S}: S\cap T=\emptyset\}$.
For a set $Z\subseteq U-T$, let $h(Z)$ denote the minimum number of sets from $\mathcal{S}_T$
needed to cover $Z$. We will assume $\mathcal{S}$ contains all singleton sets, so that
$h(Z)$ is always well defined.
Define functions $f,g:2^{\mathcal{S}}\rightarrow \mathbb{R}_{\geq 0}$ in the following manner.
For $X\subset \mathcal{S}$, $f(X)=|X| + h(u(X)-T)$ and $g(X)=|u(X)\cap T|$.

\begin{claim}
Suppose $X\subseteq\mathcal{S}$ such that $g(X)=|T|$. Then, there exists a solution $(X, Y)$
to the SSP problem with cost equal to $f(X)$. The converse also holds.
\end{claim}
\begin{proof}
Since $g(X)=|T|$, we have $T\subseteq u(X)$. Let $Y\subseteq \mathcal{S}_T$
such that $u(X)-T \subseteq u(Y)$, and $|Y|$ is minimized.
Such a $Y$ exists, and $|Y|=h(u(X)-T)$. Also, by construction, $u(Y)\cap T=\emptyset$.
Therefore,
\[
T = u(X) - u(Y),
\]
and $|X|+|Y| = f(X)$.
\end{proof}

\section{Preliminaries and problem formulation}

\subsection{Notation}
Let $U=\{x_1,\ldots,x_n\}$ denote a ground set, and let 
$\mathcal{S}=\{S_1,\ldots,S_m\}\subset 2^U$ denote a set of subsets of $U$. 
We assume that $\{x_1\},\ldots,\{x_n\}\in\mathcal{S}$, i.e., all the singleton
sets are in the set system.
Let $C(i_1,\ldots,i_k) = S_{i_1}\cap S_{i_2}\ldots\cap S_{i_k}$, where
each $S_{i_j}\in \mathcal{S}$. We refer to $C(i_1,\ldots,i_k)$ as a ``clause''.
Let $\intS_k=\{C(i_1,\ldots,i_{k'}): i_j\leq m, k'\leq k\}$
denote the set of all intersections of at most $k$ sets from $\mathcal{S}$.
We consider representations of a subset $T\subseteq U$ of the following form:
\[
T = \cup_{\ell=1}^r C(i^{\ell}_1,\ldots,i^{\ell}_{k_{\ell}}) - 
 \cup_{\ell=r+1}^s C(i^{\ell}_1,\ldots,i^{\ell}_{k_{\ell}}),
\]
where $C(i^{\ell}_1,\ldots,i^{\ell}_{k_{\ell}})\in \intS_k$.
We say the clauses $C(i^{\ell}_1,\ldots,i^{\ell}_{k_{\ell}})$ for $\ell\leq r$
are ``positive'', whereas, those for $\ell=r+1,\ldots,s$ are ``negative''.
For $C=C(i_1,\ldots,i_{k'})\in \intS_k$, we define $\cost(C)=k'$ as the
number of sets whose intersection defines $C$.
For a representation of $T$ of the above type, we associate
a cost $\alpha\sum_{\ell=1}^r k_{\ell} + \beta \sum_{\ell=r+1}^s k_{\ell}$,
where $\alpha$ and $\beta$ are parameters. 

\noindent
\textbf{Exact and approximate representations.}
The representation of the form above, where $T$ is equal to the difference of
unions of clauses, is said to be an \emph{exact} representation.
We consider the natural \emph{approximate} representations, where 
$T$ is ``close'' to $\cup_{\ell=1}^r C(i^{\ell}_1,\ldots,i^{\ell}_{k_{\ell}}) -
 \cup_{\ell=r+1}^s C(i^{\ell}_1,\ldots,i^{\ell}_{k_{\ell}})$.
\smallskip

\subsection{Problems}
\noindent
\textbf{1. Set summarization problem} (SSP). Given an instance $(U, \mathcal{S}, T, k)$,
the objective is to find a representation
\[
T = \cup_{\ell=1}^r C(i^{\ell}_1,\ldots,i^{\ell}_{k_{\ell}}) - 
 \cup_{\ell=r+1}^s C(i^{\ell}_1,\ldots,i^{\ell}_{k_{\ell}}),
\]
such that the cost 
$\alpha\sum_{\ell=1}^r k_{\ell} + \beta \sum_{\ell=r+1}^s k_{\ell}$ is minimized.

\noindent
\textbf{2. Positive version of the Set summarization problem} (positive-SSP). 
In this restriction, we consider representations consisting of only positive clauses, i.e.,
\[
T = \cup_{\ell=1}^r C(i^{\ell}_1,\ldots,i^{\ell}_{k_{\ell}}),
\]
so that the cost $\alpha\sum_{\ell=1}^r k_{\ell}$ is minimized.


\noindent
\textbf{3. Approximate version of the Set summarization problem
with false negatives} (approx-SSP-fn). 
In this version, the objective is to find a representation for a set $T'\subseteq T$ such that
\[
T' = \cup_{\ell=1}^r C(i^{\ell}_1,\ldots,i^{\ell}_{k_{\ell}}) - 
 \cup_{\ell=r+1}^s C(i^{\ell}_1,\ldots,i^{\ell}_{k_{\ell}}),
\]
such that $|T'|\geq (1-\epsilon)|T|$, and $\cost(T')$ is minimized.

\noindent
\textbf{4. Approximate version of the Set summarization problem
with false positives and false negatives} (approx-SSP). 

\subsection{More general formulation}

We have $p$ groups of sets $\mathcal{S}_j=\{S_{j1},\ldots,S_{jm_j}\}$, for $j=1,\ldots,p$.
Let $\mathcal{R}_j=\{R_{ji_1},\ldots,R_{ji_j}\}\subseteq\mathcal{S}_j$ 
be a subset of the $j$th group. Let $\elt(\mathcal{R}_j) = \cup_{R\in \mathcal{R}_j} R$
denote the union of the sets in $\mathcal{R}_j$.
A hyperset is denoted by $\mathcal{R}=(\mathcal{R}_1,\ldots,\mathcal{R}_p)$,
and consists of the following elements
\[
\cap_{j=1}^p \elt(\mathcal{R}_j)
\]

The cost $\cost(\mathcal{R})$ of such a hyperset is taken to be
\[
\cost(\mathcal{R}) = \sum_{j=1}^p |\mathcal{R}_j| = \sum_{j=1}^p i_j
\]

We consider representations of a (target) subset $T\subseteq U$ of the following form:
\[
T = \cup_{\ell=1}^r \mathcal{R}^{\ell} - \cup_{\ell=r+1}^s \mathcal{R}^{\ell},
\]
i.e., a difference of unions of hypersets. The cost of such a representation is
\[
\sum_{\ell=1}^s\cost(\mathcal{R}^{\ell})
\]

\noindent
\textbf{Generalization of Set Cover.}
The set cover problem is a special case of the above formulation, with a single group
$\mathcal{S}=\mathcal{S}_1$, so that a hyperset is an individual set $R\in\mathcal{S}$.

\noindent
\textbf{Generalization of \cite{xiang:dmkd2011}.}
The formulation above generalizes the 2-dimensional setting considered by
\cite{xiang:dmkd2011} in the following manner. The input consists of a set
$\mathcal{T}$ of $n_t$ transactions and a set $\mathcal{I}$ of $n_i$ items.
For $T\subset\mathcal{T}$ and $I\subset\mathcal{I}$,
a hyper-rectangle $H=T\times I=\{(i, j): i\in T, j\in I\}$.

Consider a universe $U=\{(i, j): i\in \mathcal{T}, j\in\mathcal{I}\}$ of $n_tn_i$ elements.
We have two groups of sets:
(1) $\mathcal{S}_1$ has a set $\{(i, j): j\in \mathcal{I}\}$ for each transaction 
$i\in\mathcal{T}$, and
(2) $\mathcal{S}_2$ has a set $\{(i, j): i\in \mathcal{T}\}$ for each item $i\in\mathcal{I}$.

\section{Related work}

The work of Xiang et al. \cite{xiang:dmkd2011} is directly related, and can be
considered as a special case of positive-SSP. The data comes from a transactional database,
where we have sets $\mathcal{I}$ and $\mathcal{T}$ of items and transactions, respectively.
Let $n_I=|\mathcal{I}|$ and $n_T=|\mathcal{T}|$. Then, the database
can be represented as a 0/1 matrix of dimensions $n_I\times n_T$.
The ground set $U$ is the set of all the matrix elements.
The set system $\mathcal{S}$ consists of all sets of the form
$T=\{i_1,\ldots,i_r\}\times\{t_1,\ldots,t_s\}$, where $\{i_1,\ldots,i_r\}\subset\mathcal{I}$
and $\{t_1,\ldots,t_s\}\subset\mathcal{T}$; these are referred to as 
``hyperrectangles'', and $\cost(T)=r+s$.
Xiang et al. give a logarithmic approximation for the positive-SSP problem
for such instances.

\section{Questions and results}

\begin{enumerate}
\item
SSP vs positive-SSP: for the 2D case \cite{xiang:dmkd2011}, 
we can construct a set $S$ corresponding to a rectangle of 1's with a single 0,
such that the optimum solution of positive-SSP version is close to three times
the optimum solution of the SSP version.
Can this gap be made larger for general SSP instances?
\item
The set system in \cite{xiang:dmkd2011} has bounded VC-dimension for ``most'' sets. 
Can we use this to improve the logarithmic approximation factor?
\item
Stronger hardness for SSP, compared to positive-SSP
\item
Logarithmic approximation for positive-SSP, at least when $k$ is bounded.
\end{enumerate}

\section{Approximation results}

\subsection{Set cover version}

We consider the approximation algorithm for the single group case, which 
is the set cover generalization. We use a simple LP rounding approach.

Let $\mathcal{S} = \{S_1,\ldots,S_m\}$ denote the $m$ sets. We have variables
$x(S)$ and $y(S)$ corresponding to the set $S$ being used in a positive and negative 
sense, respectively. We have the following LP

\begin{eqnarray*}
\min \sum_S x(S) + y(S) && \text{s.t.}\\
\forall i\in T,\ \sum_{S\ni i} x(S) &\geq& 1\\
\forall i\not\in T, S\ni i,\ \sum_{S'\ni i} y(S') &\geq& x(S)\\
\forall i\in T, S\ni i,\ y(S) &=& 0\\
\forall S,\ x(S), y(S) &\geq& 0
\end{eqnarray*}

Let $f=\max_i |\{S: i\in S\}|$ be the maximum number of sets containing any element.
Our algorithm rounds the fractional variables $x(S), y(S)$ to integral variables
$X(S), Y(S)$ in the following steps.
\begin{enumerate}
\item
For each $S$, if $x(S)\geq 1/f$, round it to 1, i.e., set 
variable $X(S)=1$. Otherwise, $X(S)=0$.
\item
For each $S$, round $y(S)$ to 1 with probability 
$\min\{1, 16f{\epsilon^2}\log{mn}\cdot y(S)\}$.
\end{enumerate}

\begin{lemma}
The rounded integral solution $X(\cdot), Y(\cdot)$ is feasible and has
cost at most $O(f\log{m} OPT)$, where $OPT$ is the cost of the optimal solution,
with probability at least $1-\frac{1}{mn}$.
\end{lemma}

\begin{proof}
For each $i\in T$, there exists at least one $S\ni i$ such that $x(S)\geq 1/f$,
by definition of $f$. Therefore, by our rounding step, 
for each $i\in T$, we have $\sum_{S\ni i} X(S)\geq 1$, and
$X(S)\leq f\cdot x(S)$.

Next, consider any $i\not\in T$ and $S\ni i$. We have
$\sum_{S'\ni i} fy(S') \geq X(S)$. We only consider constraints with $X(S)=1$; 
else, the constraint is automatically satisfied after the rounding.
Let $y'(S') = \min\{1, 16f{\epsilon^2}\log{mn}\cdot y(S)\}$.
Then, we have $\sum_{S'\ni i} y'(S') \geq 16\epsilon^2\log{mn}$.
$Y(S')$ is a random variable which is 1 with probability $y'(S')$. 
We ignore any constraint which has $y'(S')=1$ for some $S'$, since $Y(S')=1$,
and such a constraint would be automatically satisfied.

Therefore,
$E[Y(S')] = y'(S')$, and $E[\sum_{S'\ni i} Y(S')] \geq 16\epsilon^2\log{mn}$.

It follows by randomized rounding, that if
we round $y(S')$ to 1 with probability $\min\{1, cf\log{m} y(S')\}$, then with high
probability, we have $\sum_{S'\ni i} Y(S')\geq X(S)$
\end{proof}

\newpage

\section{Submodularity}

Let $S = \{S_1, S_2, ..., S_m\}$ be a collection of subsets of the ground set $U = \{x_1,  ..., x_n \}$.  Let $T$ be a target set such that $T \subseteq U$. Let $X, Y$ be subsets of $S$.

\begin{definition}
Let $S_T$ be a collection of subsets in $S$ such that 
\begin{equation}
	S_T = \{ S_i \in S : S_i \cap T = \phi \} \nonumber
\end{equation}
i.e., it consists of all subsets of $S$ that are disjoint with $T$
\end{definition}
\begin{definition}
 Let $v(X)$ be the union of all subsets in $X$ i.e.,
 \begin{equation}
 		v(X) = \cup_{S_i \in X} \; S_i  \nonumber
 \end{equation}
\end{definition}
\begin{definition}
	For any $T \subseteq U$, let  $cov(T)$ be defined as the minimum number of sets from $S_T$ needed to cover all elements of $T$, i.e.,
	\begin{equation}
		 	cov(T) = \min_{Z: Z \subseteq S, T- v(Z) = \phi} \; |Z|
	\end{equation}
\end{definition}
\begin{definition}
	Let $f \colon 2^S \to \mathbb{Z}$ be a function defined as $f(X) = |X| + cov( v(X) - T)$, i.e., sum of the number of subsets in $X$ and the minimum number of subsets needed to cover all elements in $v(X) - T$.
\end{definition}
\begin{lemma}
	The function $f$ is submodular.
\end{lemma}

\begin{definition}
	Let $g \colon 2^S \to \mathbb{Z}$ be a function defined as $g(X) = | v(X) \cap T|$, i.e, number of elements of $T$ covered by elements in $X$. 
\end{definition}

\begin{lemma}
	The function $g$ is submodular.
\end{lemma}
\begin{proof}

\end{proof}
\newpage
 
\bibliographystyle{plain}
\bibliography{references}

\end{document}

 
